Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-08-22 analysis/paper/paper.Rmd
Address Reviewer #1's comment, sentence clarity
First pass at addressing clarity issues as per Reviewer #1 comments

A custom function, `import_notes()`, was written to import the data and format the columns properly R [@RCT2022].
Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardize the capitalization and alleviate any issues with capitalization used between evaluators.

@@

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative family allows for the probability of a given value is the probability of that value or any smaller value.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log point-wise predictive density via `loo_compare()`.

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 to predict two responses with publishing journal, as the journals' abbreviation, the formula took the form: response \~ abbreviation (model 1: code_availability \~ abbreviation and model 2: data_availability \~ abbreviation) and the models included assignee as a random effect (formula: \~1 \| assignee).
Models 3 and 4 to predict the two responses with year (formula: response \~ year) and the models included abbreviation and assignee as random effects (formula: list(\~1 \| abbreviation, \~1 \| assignee)).
Models 5 and 6 to predict the two responses with IF_5year the formula took the form: response \~ IF_5year and included assignee as random effect (formula: \~1 \| assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.

>>>>

A custom function, `import_notes()`, was written to import the data and format the columns properly in R [@RCT2022].
Values for software packages were checked for spelling consistency and corrections were made manually where necessary.
When working with these data in R, all strings of software character values were converted to fully upper-case to standardize the capitalization and alleviate any issues with capitalization used between evaluators.

@@

We fitted Bayesian logistic mixed models (estimated using MCMC sampling with 4 chains of 10000 iterations and a warm-up of 5000 and thinning of 1) using cumulative family function with a logit link for ordinal data using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021].
The cumulative logit family is often used for ordinal data as it uses cumulative probabilities up to a threshold, making all of the of ordinal categories binary at that threshold.
Priors were selected to be weakly informative and deemed suitable through using `pp_check()` to examine the models' predictions based on priors only (using the parameter `sample_prior = only` in `brm()`).
Priors over all parameters were set as: normal (mean = 0.00, SD = 1.0) distributions for both fixed parameters and random effects.
The best fitting models were selected by using Widely Applicable Information Criterion (WAIC) and the expected log point-wise predictive density via `loo_compare()`.

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 were used to predict responses with publishing journal, using the journals' abbreviation as the predictor the formula took the form: response \~ abbreviation (model 1: code_availability \~ abbreviation and model 2: data_availability \~ abbreviation) and the models included assignee as a random effect (formula: \~1 \| assignee).
Models 3 and 4 were used to predict the two responses with year as the predictor (formula: response \~ year) and the models included abbreviation and assignee as random effects (formula: list(\~1 \| abbreviation, \~1 \| assignee)).
Models 5 and 6 were used to predict the responses using IF_5year as the predictor the formula took the form: response \~ IF_5year and included assignee as random effect (formula: \~1 \| assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.
